Automated assessment of residual plots with computer vision models

### 2024-05-27 paper/appendix.Rmd
wait for review

---
title: |
  Appendix: Automated assessment of residual plots with computer vision models
type: Draft paper (Incomplete)
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: Dianne Cook
    affil: a
    email: dicook@monash.edu
  - name: Emi Tanaka
    affil: b, c
    email: emi.tanaka@anu.edu.au
  - name: Susan VanderPlas
    affil: d
    email: susan.vanderplas@unl.edu
  - name: Klaus Ackermann
    affil: a
    email: Klaus.Ackermann@monash.edu
affiliation:
  - num: a
    address: |
      Department of Econometrics and Business Statistics, Monash University, Clayton, VIC, Australia
  - num: b
    address: |
      Biological Data Science Institute, Australian National University, Acton, ACT, Australia
  - num: c
    address: |
      Research School of Finance, Actuarial Studies and Statistics, Australian National University, Acton, ACT, Australia
  - num: d
    address: |
      Department of Statistics, University of Nebraska, Lincoln, Nebraska, USA
bibliography: ref.bib
abstract: |
  TBD.
keywords: |
  TBD
header-includes: |
  \usepackage{lscape}
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{setspace}
  \doublespacing
output: rticles::tf_article
editor_options: 
  chunk_output_type: console
---

@@

# Additional details about data generation

## Computation of scagnostics

In Section \ref{introduction}, we mentioned that scagnostics consist of a set of manually designed visual feature extraction functions. While our computer vision model will learn its own feature extraction function during training, leveraging additional information from scagnostics can enhance the model's predictive accuracy.

For each generated residual plot, we computed four scagnostics – "Monotonic," "Sparse," "Splines," and "Striped" – using the `cassowaryr` R package [@mason2022cassowaryr]. These computed measures, along with the number of observations from the fitted model, were provided as the second input for the computer vision model. Although other scagnostics are informative, they are currently unavailable due to a fatal bug in the compiled C program of the `interp` R package [@Albrecht2023interp], which may unpredictably crash the process. For reproducibility, we excluded these scagnostics from the training data.

@@

This study employs seven types of neural network layers, all of which are standard components frequently found in modern deep learning models. These layers are well-documented in textbooks like @goodfellow2016deep, which offer thorough explanations and mathematical insights. In this section, we will offer a concise overview of these layers, drawing primarily from the insights provided in @goodfellow2016deep.

@@

The Dense layer, also known as the fully-connected layer, is the fundamental unit in neural networks. It conducts a matrix multiplication operation between the input matrix $\boldsymbol{X}$ and a weight matrix $\boldsymbol{W}$ to generate the output matrix $\boldsymbol{O}$, which can be written as

$$\boldsymbol{O} = \boldsymbol{X}\boldsymbol{W} + b,$$

@@

$$\boldsymbol{O}(i,j) = max\{0, \boldsymbol{X}(i,j)\},$$

where $\boldsymbol{O}(i,j)$ is the $i$th row and $j$th column entry of matrix $\boldsymbol{O}$, and $\boldsymbol{X}(i,j)$ is the $i$th row and $j$th column entry of matrix $\boldsymbol{X}$.

@@

In Dense layers, matrix multiplication leads to each output unit interacting with every input unit, whereas convolutional layers operate differently with sparse interactions. Here, an output unit in a convolutional layer is connected solely to a subset of input units, and the weight is shared across all input units. Achieving this involves using a kernel, typically a small square matrix, to conduct matrix multiplication across all input units. Precisely, this concept can be formulated as:

$$O(i, j) = \sum_m\sum_nI(i - m, j - n)K(m, n),$$

@@

A pooling layer substitutes the input at a specific location with a summary statistic derived from nearby input units. Typically, there are two types of pooling layers: max pooling and average pooling. Max pooling computes the maximum value within a rectangular neighborhood, while average pooling calculates their average. Pooling layers helps making the representation approximately invariant to minor translations of the input. The output matrix of a pooling layer is approximately $s$ times smaller than the input matrix, where $s$ represents the length of the rectangular area. This can be formulated as:

$$O(i, j) = \underset{m,n}{\max} I(si + m,sj+n).$$

@@

A global pooling layer condenses an input matrix into a scalar value by either extracting the maximum or computing the average across all elements. This layer acts as a crucial link between the convolutional structure and the subsequent dense layers in a neural network architecture. When convolutional layers utilize multiple kernels, the output becomes a three-dimensional tensor with numerous channels. In this scenario, the global pooling layer treats each channel individually, much like distinct features in a conventional classifier. This approach facilitates the extraction of essential features from complex data representations, enhancing the network's ability to learn meaningful patterns.

@@

@@

<!-- ## visualize the convolutional blocks -->

>>>>

---
title: |
  Appendix: Automated assessment of residual plots with computer vision models
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: Dianne Cook
    affil: a
    email: dicook@monash.edu
  - name: Emi Tanaka
    affil: b, c
    email: emi.tanaka@anu.edu.au
  - name: Susan VanderPlas
    affil: d
    email: susan.vanderplas@unl.edu
  - name: Klaus Ackermann
    affil: a
    email: Klaus.Ackermann@monash.edu
affiliation:
  - num: a
    address: |
      Department of Econometrics and Business Statistics, Monash University, Clayton, VIC, Australia
  - num: b
    address: |
      Biological Data Science Institute, Australian National University, Acton, ACT, Australia
  - num: c
    address: |
      Research School of Finance, Actuarial Studies and Statistics, Australian National University, Acton, ACT, Australia
  - num: d
    address: |
      Department of Statistics, University of Nebraska, Lincoln, Nebraska, USA
bibliography: ref.bib
header-includes: |
  \usepackage{lscape}
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{setspace}
  \doublespacing
output: rticles::tf_article
editor_options: 
  chunk_output_type: console
---

@@

@@

This study used seven types of neural network layers, all of which are standard components frequently found in modern deep learning models. These layers are well-documented in textbooks like @goodfellow2016deep and @chollet2021deep, which offer thorough explanations and mathematical insights. In this section, we will offer a concise overview of these layers, drawing primarily from the insights provided in @goodfellow2016deep.

@@

The Dense layer, also known as the fully-connected layer, is the fundamental unit in neural networks. It conducts a matrix multiplication operation between the input matrix $\boldsymbol{I}$ and a weight matrix $\boldsymbol{W}$ to generate the output matrix $\boldsymbol{O}$, which can be written as

$$\boldsymbol{O} = \boldsymbol{I}\boldsymbol{W} + b,$$

@@

$$\boldsymbol{O}(i,j) = max\{0, \boldsymbol{I}(i,j)\},$$

where $\boldsymbol{O}(i,j)$ is the $i$th row and $j$th column entry of matrix $\boldsymbol{O}$, and $\boldsymbol{I}(i,j)$ is the $i$th row and $j$th column entry of matrix $\boldsymbol{I}$.

@@

In Dense layers, matrix multiplication leads to each output unit interacting with every input unit, whereas convolutional layers operate differently with sparse interactions. An output unit in a convolutional layer is connected solely to a subset of input units, and the weight is shared across all input units. Achieving this involves using a kernel, typically a small square matrix, to conduct matrix multiplication across all input units. Precisely, this concept can be formulated as:

$$\boldsymbol{O}(i, j) = \sum_m\sum_n\boldsymbol{I}(i - m, j - n)K(m, n),$$

@@

A pooling layer substitutes the input at a specific location with a summary statistic derived from nearby input units. Typically, there are two types of pooling layers: max pooling and average pooling. Max pooling computes the maximum value within a rectangular neighborhood, while average pooling calculates their average. Pooling layers helps making the representation approximately invariant to minor translations of the input. The output matrix of a pooling layer is approximately $s$ times smaller than the input matrix, where $s$ represents the length of the rectangular area. A max pooling layer can be formulated as:

$$\boldsymbol{O}(i, j) = \underset{m,n}{\max} \boldsymbol{I}(si + m,sj+n).$$

@@

A global pooling layer condenses an input matrix into a scalar value by either extracting the maximum or computing the average across all elements. This layer acts as a crucial link between the convolutional structure and the subsequent dense layers in a neural network architecture. When convolutional layers uses multiple kernels, the output becomes a three-dimensional tensor with numerous channels. In this scenario, the global pooling layer treats each channel individually, much like distinct features in a conventional classifier. This approach facilitates the extraction of essential features from complex data representations, enhancing the network's ability to learn meaningful patterns. A global max pooling layer can be formulated as

$$O(i, j) = \underset{m,n,k}{\max} I(si + m,sj+n,k),$$
where $k$ is the kernel index.

@@

Batch normalization is a method of adaptive reparametrization. One of the issues it adjusts is the simultaneous update of parameters in different layers, especially for network with a large number layers. At training time, the batch normalization layer normalizes the input matrix $I$ using the formula

$$\boldsymbol{O} = \frac{\boldsymbol{I} - \boldsymbol{\mu}_I}{\boldsymbol{\sigma}_I},$$

where $\boldsymbol{\mu}_I$ and $\boldsymbol{\sigma}_I$ are the mean and the standard deviation of each unit respectively.

It reparametrizes the model to make some units always be standardized by definition, such that the model training is stabilized. At inference time, $\boldsymbol{\mu}_I$ and $\boldsymbol{\sigma}_I$ are usually replaced with the running mean and running average obtained during training.

@@

Dropout is a computationally inexpensive way to apply regularization on neural network. For each input unit, it randomly sets to be zero during training, effectively training a large number of subnetworks simultaneously, but these subnetworks share weights and each will only be trained for a single steps in a large network. It is essentially a different implementation of the bagging algorithm. Mathematically, it is formulated as

$$\boldsymbol{O}(i,j) = \boldsymbol{D}(i,j)\boldsymbol{I}(i,j),$$

where $\boldsymbol{D}(i,j) \sim B(1, p)$ and $p$ is a hyperparameter that can be tuned.

### 2024-05-27 paper/appendix.tex
wait for review

\articletype{Draft paper (Incomplete)}

@@

\begin{abstract}
TBD.
\end{abstract}

\begin{keywords}
TBD
\end{keywords}

\section{Additional details about data
generation}\label{additional-details-about-data-generation}

\subsection{Computation of
scagnostics}\label{computation-of-scagnostics}

In Section \ref{introduction}, we mentioned that scagnostics consist of
a set of manually designed visual feature extraction functions. While
our computer vision model will learn its own feature extraction function
during training, leveraging additional information from scagnostics can
enhance the model's predictive accuracy.

For each generated residual plot, we computed four scagnostics --
``Monotonic,'' ``Sparse,'' ``Splines,'' and ``Striped'' -- using the
\texttt{cassowaryr} R package \citep{mason2022cassowaryr}. These
computed measures, along with the number of observations from the fitted
model, were provided as the second input for the computer vision model.
Although other scagnostics are informative, they are currently
unavailable due to a fatal bug in the compiled C program of the
\texttt{interp} R package \citep{Albrecht2023interp}, which may
unpredictably crash the process. For reproducibility, we excluded these
scagnostics from the training data.

@@

This study employs seven types of neural network layers, all of which
are standard components frequently found in modern deep learning models.
These layers are well-documented in textbooks like
\citet{goodfellow2016deep}, which offer thorough explanations and
mathematical insights. In this section, we will offer a concise overview
of these layers, drawing primarily from the insights provided in
\citet{goodfellow2016deep}.

@@

The Dense layer, also known as the fully-connected layer, is the
fundamental unit in neural networks. It conducts a matrix multiplication
operation between the input matrix \(\boldsymbol{X}\) and a weight
matrix \(\boldsymbol{W}\) to generate the output matrix
\(\boldsymbol{O}\), which can be written as

\[\boldsymbol{O} = \boldsymbol{X}\boldsymbol{W} + b,\]

@@

\[\boldsymbol{O}(i,j) = max\{0, \boldsymbol{X}(i,j)\},\]

where \(\boldsymbol{O}(i,j)\) is the \(i\)th row and \(j\)th column
entry of matrix \(\boldsymbol{O}\), and \(\boldsymbol{X}(i,j)\) is the
\(i\)th row and \(j\)th column entry of matrix \(\boldsymbol{X}\).

@@

In Dense layers, matrix multiplication leads to each output unit
interacting with every input unit, whereas convolutional layers operate
differently with sparse interactions. Here, an output unit in a
convolutional layer is connected solely to a subset of input units, and
the weight is shared across all input units. Achieving this involves
using a kernel, typically a small square matrix, to conduct matrix
multiplication across all input units. Precisely, this concept can be
formulated as:

\[O(i, j) = \sum_m\sum_nI(i - m, j - n)K(m, n),\]

@@

A pooling layer substitutes the input at a specific location with a
summary statistic derived from nearby input units. Typically, there are
two types of pooling layers: max pooling and average pooling. Max
pooling computes the maximum value within a rectangular neighborhood,
while average pooling calculates their average. Pooling layers helps
making the representation approximately invariant to minor translations
of the input. The output matrix of a pooling layer is approximately
\(s\) times smaller than the input matrix, where \(s\) represents the
length of the rectangular area. This can be formulated as:

\[O(i, j) = \underset{m,n}{\max} I(si + m,sj+n).\]

@@

A global pooling layer condenses an input matrix into a scalar value by
either extracting the maximum or computing the average across all
elements. This layer acts as a crucial link between the convolutional
structure and the subsequent dense layers in a neural network
architecture. When convolutional layers utilize multiple kernels, the
output becomes a three-dimensional tensor with numerous channels. In
this scenario, the global pooling layer treats each channel
individually, much like distinct features in a conventional classifier.
This approach facilitates the extraction of essential features from
complex data representations, enhancing the network's ability to learn
meaningful patterns.

@@

@@

>>>>

\articletype{}

@@

@@

This study used seven types of neural network layers, all of which are
standard components frequently found in modern deep learning models.
These layers are well-documented in textbooks like
\citet{goodfellow2016deep} and \citet{chollet2021deep}, which offer
thorough explanations and mathematical insights. In this section, we
will offer a concise overview of these layers, drawing primarily from
the insights provided in \citet{goodfellow2016deep}.

@@

The Dense layer, also known as the fully-connected layer, is the
fundamental unit in neural networks. It conducts a matrix multiplication
operation between the input matrix \(\boldsymbol{I}\) and a weight
matrix \(\boldsymbol{W}\) to generate the output matrix
\(\boldsymbol{O}\), which can be written as

\[\boldsymbol{O} = \boldsymbol{I}\boldsymbol{W} + b,\]

@@

\[\boldsymbol{O}(i,j) = max\{0, \boldsymbol{I}(i,j)\},\]

where \(\boldsymbol{O}(i,j)\) is the \(i\)th row and \(j\)th column
entry of matrix \(\boldsymbol{O}\), and \(\boldsymbol{I}(i,j)\) is the
\(i\)th row and \(j\)th column entry of matrix \(\boldsymbol{I}\).

@@

In Dense layers, matrix multiplication leads to each output unit
interacting with every input unit, whereas convolutional layers operate
differently with sparse interactions. An output unit in a convolutional
layer is connected solely to a subset of input units, and the weight is
shared across all input units. Achieving this involves using a kernel,
typically a small square matrix, to conduct matrix multiplication across
all input units. Precisely, this concept can be formulated as:

\[\boldsymbol{O}(i, j) = \sum_m\sum_n\boldsymbol{I}(i - m, j - n)K(m, n),\]

@@

A pooling layer substitutes the input at a specific location with a
summary statistic derived from nearby input units. Typically, there are
two types of pooling layers: max pooling and average pooling. Max
pooling computes the maximum value within a rectangular neighborhood,
while average pooling calculates their average. Pooling layers helps
making the representation approximately invariant to minor translations
of the input. The output matrix of a pooling layer is approximately
\(s\) times smaller than the input matrix, where \(s\) represents the
length of the rectangular area. A max pooling layer can be formulated
as:

\[\boldsymbol{O}(i, j) = \underset{m,n}{\max} \boldsymbol{I}(si + m,sj+n).\]

@@

A global pooling layer condenses an input matrix into a scalar value by
either extracting the maximum or computing the average across all
elements. This layer acts as a crucial link between the convolutional
structure and the subsequent dense layers in a neural network
architecture. When convolutional layers uses multiple kernels, the
output becomes a three-dimensional tensor with numerous channels. In
this scenario, the global pooling layer treats each channel
individually, much like distinct features in a conventional classifier.
This approach facilitates the extraction of essential features from
complex data representations, enhancing the network's ability to learn
meaningful patterns. A global max pooling layer can be formulated as

\[O(i, j) = \underset{m,n,k}{\max} I(si + m,sj+n,k),\] where \(k\) is
the kernel index.

@@

Batch normalization is a method of adaptive reparametrization. One of
the issues it adjusts is the simultaneous update of parameters in
different layers, especially for network with a large number layers. At
training time, the batch normalization layer normalizes the input matrix
\(I\) using the formula

\[\boldsymbol{O} = \frac{\boldsymbol{I} - \boldsymbol{\mu}_I}{\boldsymbol{\sigma}_I},\]

where \(\boldsymbol{\mu}_I\) and \(\boldsymbol{\sigma}_I\) are the mean
and the standard deviation of each unit respectively.

It reparametrizes the model to make some units always be standardized by
definition, such that the model training is stabilized. At inference
time, \(\boldsymbol{\mu}_I\) and \(\boldsymbol{\sigma}_I\) are usually
replaced with the running mean and running average obtained during
training.

@@

Dropout is a computationally inexpensive way to apply regularization on
neural network. For each input unit, it randomly sets to be zero during
training, effectively training a large number of subnetworks
simultaneously, but these subnetworks share weights and each will only
be trained for a single steps in a large network. It is essentially a
different implementation of the bagging algorithm. Mathematically, it is
formulated as

\[\boldsymbol{O}(i,j) = \boldsymbol{D}(i,j)\boldsymbol{I}(i,j),\]

where \(\boldsymbol{D}(i,j) \sim B(1, p)\) and \(p\) is a hyperparameter
that can be tuned.

### 2024-05-27 paper/cnn.tex
wait for review

\def\ConvColor{rgb:yellow,5;red,2.5;white,5}
\def\ConvReluColor{rgb:yellow,5;red,5;white,5}
\def\PoolColor{rgb:red,1;black,0.3}
\def\FcColor{rgb:blue,5;red,2.5;white,5}
\def\FcReluColor{rgb:blue,5;red,5;white,5}
\def\SoftmaxColor{rgb:magenta,5;black,7}
\def\AuxColor{rgb:blue,5;green,15;white,5}
\def\AuxReluColor{rgb:blue,5;green,7.5;white,5}

@@

% conv1_1,conv1_2
\pic[shift={(0,0,0)}] at (0,0,0) {RightBandedBox={name=cr1,caption=Convolutional block 1,%
        xlabel={{"32","32"}},ylabel=32,zlabel=32,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=40,width={2,2},depth=40}};
%pool1
\pic[shift={(0,0,0)}] at (cr1-east) {Box={name=p1,%
        fill=\PoolColor,opacity=0.5,height=35,width=1,depth=35}};
%%%%%%%%%%
% conv2_1,conv2_2
\pic[shift={(2,0,0)}] at (p1-east) {RightBandedBox={name=cr2,caption=Convolutional block 2,%
        xlabel={{"64","64"}},zlabel=16,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=35,width={3,3},depth=35}};
%pool2
\pic[shift={(0,0,0)}] at (cr2-east) {Box={name=p2,%
        fill=\PoolColor,opacity=0.5,height=30,width=1,depth=30}};
%%%%%%%%%%
% conv3_1,conv3_2
\pic[shift={(2,0,0)}] at (p2-east) {RightBandedBox={name=cr3,caption=Convolutional block 3,%
        xlabel={{"128","128","128"}},zlabel=8,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=30,width={4,4,4},depth=30}};
%pool3
\pic[shift={(0,0,0)}] at (cr3-east) {Box={name=p3,%
        fill=\PoolColor,opacity=0.5,height=23,width=1,depth=23}};
%%%%%%%%%%
% conv4_1,conv4_2,conv4_3
\pic[shift={(1.8,0,0)}] at (p3-east) {RightBandedBox={name=cr4,caption=Convolutional block 4,%
        xlabel={{"256","256","256"}},zlabel=4,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=23,width={7,7,7},depth=23}};
%pool4
\pic[shift={(0,0,0)}] at (cr4-east) {Box={name=p4,%
        fill=\PoolColor,opacity=0.5,height=15,width=1,depth=15}};
%%%%%%%%%%
% conv5_1,conv5_2,conv5_3
\pic[shift={(1.5,0,0)}] at (p4-east) {RightBandedBox={name=cr5,caption=Convolutional block 5,%
        xlabel={{"256","256","256"}},zlabel=2,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=15,width={7,7,7},depth=15}};
%pool5
\pic[shift={(0,0,0)}] at (cr5-east) {Box={name=p5,%
        fill=\PoolColor,opacity=0.5,height=10,width=1,depth=10}};
%%%%%%%%%%
% fc6
\pic[shift={(3,0,0)}] at (p5-east) {Box={name=fc6,caption=Concatenation layer,%
        xlabel={{"1",""}},zlabel=256,fill=\FcColor,%
        height=3,width=3,depth=100}};

>>>>

\def\ConvColor{rgb:yellow,5;red,2.5;white,5}
\def\ConvReluColor{rgb:yellow,5;red,5;white,5}
\def\PoolColor{rgb:red,1;black,0.3}
\def\ConColor{rgb:black,1;white,1}
\def\FcColor{rgb:blue,5;red,2.5;white,5}
\def\FcReluColor{rgb:blue,5;red,5;white,5}
\def\SoftmaxColor{rgb:magenta,5;black,7}
\def\AuxColor{rgb:blue,5;green,15;white,5}
\def\AuxReluColor{rgb:blue,5;green,7.5;white,5}

@@

% conv1_1,conv1_2
\pic[shift={(0,0,0)}] at (0,0,0) {RightBandedBox={name=cr1,caption=Convolutional block 1,%
        xlabel={{"32","32"}},ylabel=32,zlabel=32,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=40,width={2,2},depth=40}};
%pool1
\pic[shift={(0,0,0)}] at (cr1-east) {Box={name=p1,%
        fill=\PoolColor,opacity=0.5,height=35,width=1,depth=35}};
%%%%%%%%%%
% conv2_1,conv2_2
\pic[shift={(2,0,0)}] at (p1-east) {RightBandedBox={name=cr2,caption=Convolutional block 2,%
        xlabel={{"64","64"}},zlabel=16,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=35,width={3,3},depth=35}};
%pool2
\pic[shift={(0,0,0)}] at (cr2-east) {Box={name=p2,%
        fill=\PoolColor,opacity=0.5,height=30,width=1,depth=30}};
%%%%%%%%%%
% conv3_1,conv3_2
\pic[shift={(2,0,0)}] at (p2-east) {RightBandedBox={name=cr3,caption=Convolutional block 3,%
        xlabel={{"128","128","128"}},zlabel=8,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=30,width={4,4,4},depth=30}};
%pool3
\pic[shift={(0,0,0)}] at (cr3-east) {Box={name=p3,%
        fill=\PoolColor,opacity=0.5,height=23,width=1,depth=23}};
%%%%%%%%%%
% conv4_1,conv4_2,conv4_3
\pic[shift={(1.8,0,0)}] at (p3-east) {RightBandedBox={name=cr4,caption=Convolutional block 4,%
        xlabel={{"256","256","256"}},zlabel=4,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=23,width={7,7,7},depth=23}};
%pool4
\pic[shift={(0,0,0)}] at (cr4-east) {Box={name=p4,%
        fill=\PoolColor,opacity=0.5,height=15,width=1,depth=15}};
%%%%%%%%%%
% conv5_1,conv5_2,conv5_3
\pic[shift={(1.5,0,0)}] at (p4-east) {RightBandedBox={name=cr5,caption=Convolutional block 5,%
        xlabel={{"256","256","256"}},zlabel=2,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=15,width={7,7,7},depth=15}};
%pool5
\pic[shift={(0,0,0)}] at (cr5-east) {Box={name=p5,%
        fill=\PoolColor,opacity=0.5,height=10,width=1,depth=10}};
%%%%%%%%%%
% fc6
\pic[shift={(3,0,0)}] at (p5-east) {Box={name=fc6,caption=Concatenation layer,%
        xlabel={{"1",""}},zlabel=256,fill=\ConColor,%
        height=3,width=3,depth=100}};
